Computational methods in landscape ecology

### 2024-09-18 Manuscript.qmd
Update gitignore and manuscript.qmd

author:
  - name: Maximilian H.K. Hesselbarth
    orcid: 0000-0003-1125-9918
    email: mhk.hesselbarth@gmail.com
    affil-id: 1
    attributes:
      - corresponding: boolean
  - name: Jakub Nowosad
    orcid: 0000-0002-1057-3721
    email: nowosad.jakub@gmail.com
    affil-id: 2,3
  - name: Martí Bosch
    orcid: 0000-0001-8735-9144
    email: marti.bosch@epfl.ch
    affil-id: 4
  - name: Martin Jung
    orcid: 0000-0002-7569-1390
    email: jung@iiasa.ac.at
    affil-id: 1
  - name: Alida de Flamingh
    orcid: 0000-0003-1223-6654
    email: adeflamingh@gmail.com
    affil-id: 5

affiliations: 
  - id: 1
    name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg, Austria
  - id: 2
    name: Adam Mickiewicz University, Poznań, Poland
  - id: 3
    name: University of Münster, Münster, Germany
  - id: 4
    name: École polytechnique fédérale de Lausanne, Lausanne, Switzerland
  - id: 5
    name: Carl R. Woese Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA

>>>>

author:
  - name: Maximilian H.K. Hesselbarth
    orcid: 0000-0003-1125-9918
    email: mhk.hesselbarth@gmail.com
    affil-id: 1
    attributes:
      - corresponding: boolean
  - name: Jakub Nowosad
    orcid: 0000-0002-1057-3721
    email: nowosad.jakub@gmail.com
    affil-id: 2,3
  - name: Martí Bosch
    orcid: 0000-0001-8735-9144
    email: marti.bosch@epfl.ch
    affil-id: 4
  - name: Martin Jung
    orcid: 0000-0002-7569-1390
    email: jung@iiasa.ac.at
    affil-id: 1
  - name: Alida de Flamingh
    orcid: 0000-0003-1223-6654
    email: adeflamingh@gmail.com
    affil-id: 5
  - name: Gemma Gerber
    orcid: 0000-0002-8722-3113
    email: gerber@iiasa.ac.at
    affil-id: 1
  - name: Craig E. Simpkins
    orcid: 0000-0003-3212-1379
    email: simpkinscraig063@gmail.com
    affil-id: 6

affiliations: 
  - id: 1
    name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg, Austria
  - id: 2
    name: Adam Mickiewicz University, Poznań, Poland
  - id: 3
    name: University of Münster, Münster, Germany
  - id: 4
    name: École polytechnique fédérale de Lausanne, Lausanne, Switzerland
  - id: 5
    name: Carl R. Woese Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA
  - id: 6
    name: Auckland Council, Environmental Services Department, Auckland, New Zealand
